A thesis draft

### 2018-12-05 thesis/res/sections/11-ProjectScheduling.tex
Presentation integration (#18)
Integrate presentation in thesis repository

Before starting this project a time requirements has been carried out, to see
its feasibility. We calculated at least six month necessary to be able to create
a working proof of concept (PoC) that allowed us to perform tests and, in
general, to have a feedback about the solution.

\subsection{Scheduled timeline}
Since our knowledge about the technologies was very poor at the beginning, we
preferred to invest a good chunk of time on studying them, to understand the already
present products available in the market and to choose what we really needed.
Additionally, at the end of this phase we though it was necessary to try these
products to see if they really fitted our necessities. After this phase, we
planned to actually starting implementing the missing components to create and
to fulfill the requirements defined in Section~\ref{chap:prjan:sec:req}. Since
the required technologies, Java and C/C++ are known to the authors, we estimated
an eight-week period related to coding and software implementation. After that,
a two weeks were planned in order to perform tests and gather metrics about the
system built, and too see how much the job done satisfied our expectations.
Finally, we estimated four weeks to group and write down all the information and
considerations we got during the thesis.

\subsection{Actual timeline}
Unfortunately, many difficulties slowed our project development, starting from
the beginning. The total time required to finish all the requirements decided
was of 37 weeks, namely nine months circa. Many problems emerged during the
study of the technologies, that revealed to be more complicated than expected,
especially since some frameworks were more complicated to deploy and try them
out. Time was lost to obtain resources from the University that was not
initially planned. On top of that, we encountered little bugs we had to manually
fix, like for example in the Floodlight Controller\footnote{See
  \url{https://github.com/floodlight/floodlight-webui/pull/10}}, that
additionally slowed our technologies exploration. This not-planned digging in
other projects' code cost us time and resources, delaying this phase of eight
weeks, for a total of 17 weeks. The software implementation revealed to be
irksome too. We end up underestimating the time required for this phase, because
we did not consider all the issues related to work with system calls. Moreover,
we had to implement more components than planned, in order to be able to
actually transmit data between two senders. In a nutshell, the additional time
required was of eight weeks, for a total of 16 weeks. Finally, the time to write
down the following thesis was limited due, and we had to write it down in a
total of two weeks, instead of the four initially planned.

>>>>

Before starting this project a time scheduling has been carried out, to see
its feasibility. We calculated at least six months necessary to be able to create
a working proof of concept (PoC) that allowed us to perform tests and, in
general, to have a feedback about the solution.

\subsection{Scheduled timeline}
Since our knowledge about the technologies was very poor at the beginning, we
preferred to invest a good chunk of time on studying them, to understand the
already present products available in the market and to choose what we really
needed. Additionally, at the end of this phase we though it was necessary to try
these products to see if they really fitted our necessities. After this phase,
we planned to actually starting implementing the missing components to create
and to fulfill the requirements defined in Section~\ref{chap:prjan:sec:req}.
Since the required technologies, Java and C/C++ are known to the authors, we
estimated an eight-week period related to coding and software implementation.
After that, two weeks were planned in order to perform tests and gather metrics
about the system built, and too see how much the job done satisfied our
expectations. Finally, we estimated four weeks to group and write down all the
information and considerations we got during the thesis.

\subsection{Actual timeline}
Unfortunately, many difficulties slowed our project development, starting from
the beginning. The total time required to finish all the planned requirements
was of 37 weeks, namely nine months circa. Many problems emerged during the
study of the technologies, that revealed to be more complicated than expected,
especially since some frameworks were more intricate to deploy and to try them
out. Time was lost to obtain resources from the University that was not
initially planned. On top of that, we encountered little bugs we had to manually
fix, like for example in the Floodlight Controller\footnote{See
  \url{https://github.com/floodlight/floodlight-webui/pull/10}}, that
additionally slowed our technologies exploration. This not-planned digging in
other projects' code cost us time and resources, delaying this phase of eight
weeks, for a total of 17 weeks. The software implementation revealed to be
irksome too. We end up underestimating the time required for this phase, because
we did not consider all the issues related to work with system calls. Moreover,
we had to implement more components than planned, in order to be able to
actually transmit data between two senders. In a nutshell, the additional time
required was of eight weeks, for a total of 16 weeks. Finally, the time to write
down the following thesis was limited too, and we had to write it down in a
total of two weeks, instead of the four initially planned.

### 2018-12-05 thesis/res/sections/20-VNFImplementaton.tex
Presentation integration (#18)
Integrate presentation in thesis repository

The complexity behind the creation of a working Service Function Chain system
was so high to require particular care and a separated study. Indeed, the SFCs
are the at the base of the whole architecture: packet transmission and
elaboration is made here. Challenges regarding this topic are building a system
that is flexible enough to allow dynamic packet routing, support scalability and
provide methods to recovery from failures. In this chapter, a brief explanation
about the challenges and the issues encountered building this system will be
given.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{finalreview}
  \caption{Final review schema}
  \label{chap:impl:img:finalreview}
\end{figure}

The approved proposal for the creation of a proper chain has been based on four components:
\begin{itemize}
\item Astaire, which aim is to performing packet encapsulation and decapsulation
  between VNFs;
\item Harbor, which acts as our MANO component;
\item Ironhide, that provides ingress and egress point from our architecture;
\item Roulette, that stores endpoint information and holds the SFC topology
  view.
\end{itemize}

@@

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
preserved, so that VNFs can perform packet elaboration. In order to obtain this,
packet encapsulation has been used. IP in IP encapsulation allows to preserve
the original packet, making the incoming packet the payload of a new one.

>>>>

The complexity behind the creation of a working Service Function Chain system
was high demanding for particular care and a separated study. Indeed, the SFCs
are the at the core of the whole architecture: packet transmission and
elaboration is made here. Challenges regarding this topic are building a system
that is flexible enough to allow dynamic packet routing, support scalability and
provide methods to recovery from failures. In this chapter, a brief explanation
about the challenges and the issues encountered building this system are given.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{finalreview}
  \caption{Final review schema}
  \label{chap:impl:img:finalreview}
\end{figure}
In Figure~\ref{chap:impl:img:finalreview} is shown a high level schema
evidencing the components and their relationships. The approved proposal for the
creation of a proper chain has been based on four components:
\begin{itemize}
\item Astaire, which aim is to performing packet encapsulation and decapsulation
  between VNFs;
\item Harbor, which acts as our MANO component;
\item Ironhide, that provides ingress and egress point from our architecture;
\item Roulette, that stores endpoint information and holds the SFC topology
  view.
\end{itemize}

@@

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
preserved, so that VNFs can perform packet elaboration. In order to obtain this,
packet encapsulation has been used. An IP/IP encapsulation allows to preserve
the original packet, making the incoming packet the payload of a new one.

### 2018-12-05 thesis/res/sections/40-FutureWork.tex
Presentation integration (#18)
Integrate presentation in thesis repository

One of the aspects that is usually not really given the required attention is
the one regarding security. In this context, the security we talk is the one
about the whole system, and not the single VNFs implementations. Fortunately,
Kubernetes is equipped with out-of-the-box access management options. A good way
to manage user authentication in the system should be integrate the Role Based
Access model provided by Kubernetes directly in Harbor. In fact, Harbor does not
come with security features, and the exposed APIs are usable by everyone. This
could lead to possible Denial of Service (DoS) attack of the disruption of NS
services by a malicious attacker.

>>>>

One of the aspects that is usually not really given the required attention is
the one regarding security. In this context, the security we talk is the one
about the whole system, and not the single VNFs implementation. Fortunately,
Kubernetes is equipped with out-of-the-box access management options. A good way
to manage user authentication in the system should be integrate the Role Based
Access model provided by Kubernetes directly in Harbor. In fact, Harbor does not
come with security features, and the exposed APIs are usable by everyone. This
could lead to possible Denial of Service (DoS) attacks leading to the disruption
of NS services by a malicious attacker.
